Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-27 prob.tex
prob.tex \section{Proof} updating definitions...

>>>>

\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
is denoted by $S^{d-1}$.\qed\end{definition}

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called an \emph{approximation frame function} of weight~$\left(\underline{W},\overline{W}\right)$
if 
\[
\underline{W}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le\overline{W}
\]
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.\qed\end{definition}

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a frame function of weight~$\left(\underline{W},\overline{W}\right)$,
and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
defined by
\[
g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}
